Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-12 paper.qmd
Updated plot_proj

proj_obj1 <- get_projection(projection = model_prj1, 
               proj_scale = 1, 
               scaled_data = scaled_two_curvy_data, 
               scaled_data_model = scaled_two_curvy_data_model, 
               distance_df_small_edges = tr_from_to_df_two_curvy, 
               axis_param = list(limits = 0.5, 
                                 axis_scaled = 2,
                                 axis_pos_x = -0.5, 
                                 axis_pos_y = -0.5, 
                                 threshold = 0.03))

@@

two_curvy_proj_true <- plot_proj(
  proj_obj = proj_obj1_true, 
  point_param = c(0.5, 0.5, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "black"), # linewidth, alpha
  plot_limits = c(-0.6, 0.6), 
  title = "a", 
  cex = 1.5, 
  axis_text_size = 4, 
  is_color = FALSE) +
  theme(aspect.ratio=1, 
        legend.position = "none")

@@

two_curvy_proj_tsne_first_model1 <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-0.6, 0.6), 
    title = "b", 
    cex = 1, 
    position = sc_ltr_pos,
    axis_text_size = 2, 
    is_color = FALSE) +
    theme(aspect.ratio = 1,
          legend.position = "none")

@@

proj_obj2 <- get_projection(projection = model_prj2, 
                            proj_scale = 1, 
                            scaled_data = scaled_two_curvy_data, 
                            scaled_data_model = scaled_two_curvy_data_model, 
                            distance_df_small_edges = tr_from_to_df_two_curvy, 
                            axis_param = list(limits = 0.35, 
                                              axis_scaled = 2,
                                              axis_pos_x = -0.35, 
                                              axis_pos_y = -0.35, 
                                              threshold = 0.01))

@@

two_curvy_proj_true2 <- plot_proj(
    proj_obj = proj_obj2_true, 
    point_param = c(0.5, 0.5, clr_choice), # size, alpha, color
    line_param = c(0.5, 0.5, "black"), # linewidth, alpha
    plot_limits = c(-0.42, 0.42), 
    title = "b", 
    cex = 1.5, 
    axis_text_size = 4, 
    is_color = FALSE) +
    theme(aspect.ratio = 1, 
          legend.position = "none")

@@

two_curvy_proj_tsne_all_model1 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(0.1, 0.5, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "black"), # linewidth, alpha
  plot_limits = c(-0.5, 0.5), 
  title = "c", 
  cex = 1, 
  position = sc_ltr_pos,
  axis_text_size = 2, 
  is_color = FALSE) +
  theme(aspect.ratio = 1) #+
  #geom_segment(
  #  data = model_df, 
  #  aes(
  #    x = proj1_from, 
  #    y = proj2_from, 
  #    xend = proj1_to, 
  #    yend = proj2_to), 
  #  color = "#000000")

@@

algo_obj_two_curvy2 <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_two_curvy, 
  nldr_data = tsne_two_curvy, 
  num_x_bins = num_bins_x_two_curvy)

tr_from_to_df_two_curvy2 <- algo_obj_two_curvy2$tr_from_to_df
df_bin_centroids_two_curvy2 <- algo_obj_two_curvy2$df_bin_centroids
df_bin_two_curvy2 <- algo_obj_two_curvy2$df_bin
hex_grid_with_counts_two_curvy2 <- algo_obj_two_curvy2$hex_grid_with_counts

@@

tr_from_to_df_two_curvy3 <- algo_obj_two_curvy3$tr_from_to_df
df_bin_centroids_two_curvy3 <- algo_obj_two_curvy3$df_bin_centroids
df_bin_two_curvy3 <- algo_obj_two_curvy3$df_bin
hex_grid_with_counts_two_curvy3 <- algo_obj_two_curvy3$hex_grid_with_counts

@@

<!-- two_curvy_proj_first_model1_umap <- plot_proj( -->
<!--     proj_obj = proj_obj1,  -->
<!--     point_param = c(0.5, 0.2, "#636363"), # size, alpha, color -->
<!--     line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha -->
<!--     plot_limits = c(-0.6, 0.6),  -->
<!--     title = "c2",  -->
<!--     cex = 2,  -->
<!--     position = sc_ltr_pos, -->
<!--     axis_text_size = 4,  -->
<!--     is_color = FALSE) + -->
<!--     theme( -->
<!--         legend.position = "none" -->
<!--     ) -->

@@

<!-- two_curvy_proj_model_delaunay_umap <- plot_proj( -->
<!--     proj_obj = proj_obj1_temp1,  -->
<!--     point_param = c(0.5, 0.2, "#636363"), # size, alpha, color -->
<!--     line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha -->
<!--     plot_limits = c(-0.6, 0.6),  -->
<!--     title = "a2",  -->
<!--     cex = 2,  -->
<!--     position = sc_ltr_pos, -->
<!--     axis_text_size = 4,  -->
<!--     is_color = FALSE) + -->
<!--     theme(aspect.ratio = 1,  -->
<!--           legend.position = "none") -->

@@

<!-- two_curvy_proj_model_benchmark2_umap <- plot_proj( -->
<!--     proj_obj = proj_obj1_temp2,  -->
<!--     point_param = c(0.5, 0.2, "#636363"), # size, alpha, color -->
<!--     line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha -->
<!--     plot_limits = c(-0.6, 0.6),  -->
<!--     title = "b2",  -->
<!--     cex = 2,  -->
<!--     position = sc_ltr_pos, -->
<!--     axis_text_size = 4,  -->
<!--     is_color = FALSE) + -->
<!--     theme(aspect.ratio = 1,  -->
<!--           legend.position = "none") -->

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 2, 
               scaled_data = scaled_gau_data, 
               scaled_data_model = scaled_gau_data_model, 
               distance_df_small_edges = tr_from_to_df_gau1, 
               axis_param = list(limits = 1,
                                 axis_scaled = 2,
                                 axis_pos_x = -0.72, 
                                 axis_pos_y = -0.72, 
                                 threshold = 0.1))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 3, 
                            scaled_data = scaled_gau_data, 
                            scaled_data_model = scaled_gau_data_model, 
                            distance_df_small_edges = tr_from_to_df_gau1, 
                            axis_param = list(limits = 1.5,
                                              axis_scaled = 2,
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.05))

five_gau_proj_tsne_model2 <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(1.5, 0.05, clr_choice), # size, alpha, color
  line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
  plot_limits = c(-1.3, 1.3), 
  title = "a3", 
  cex = 1.5,
  position = c(0.08, 0.9),
  axis_text_size = 4, 
  is_color = FALSE) +
  theme(aspect.ratio = 1,
        legend.position = "none")
```

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 3, 
                            scaled_data = scaled_gau_data, 
                            scaled_data_model = scaled_gau_data_model, 
                            distance_df_small_edges = tr_from_to_df_gau1, 
                            axis_param = list(limits = 1.5,
                                              axis_scaled = 2,
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.05))

five_gau_proj_umap_model2 <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(1.5, 0.05, clr_choice), # size, alpha, color
  line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
  plot_limits = c(-1.3, 1.3), 
  title = "b3", 
  cex = 1.5,
  position = c(0.08, 0.9),
  axis_text_size = 4, 
  is_color = FALSE) +
  theme(aspect.ratio = 1,
        legend.position = "none")
```

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 3, 
                            scaled_data = scaled_gau_data, 
                            scaled_data_model = scaled_gau_data_model, 
                            distance_df_small_edges = tr_from_to_df_gau1, 
                            axis_param = list(limits = 1.5,
                                              axis_scaled = 2,
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.05))

five_gau_proj_pacmap_model2 <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(1.5, 0.05, clr_choice), # size, alpha, color
  line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
  plot_limits = c(-1.3, 1.3), 
  title = "c3", 
  cex = 1.5,
  position = c(0.08, 0.9),
  axis_text_size = 4, 
  is_color = FALSE) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

proj_obj1 <- get_projection(projection = projection,
                            proj_scale = 1,
                            scaled_data = scaled_c_shaped_data,
                            scaled_data_model = scaled_c_shaped_data_model,
                            distance_df_small_edges = tr_from_to_df_dens_clust,
                            axis_param = list(limits = 0.4,
                                              axis_scaled = 3,
                                              axis_pos_x = -0.28,
                                              axis_pos_y = -0.28,
                                              threshold = 0.02))

@@

five_c_shaped_proj_tsne_model1 <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "a3", 
    cex = 2,
    position = c(0.08, 0.9),
    axis_text_size = 4.5, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")

@@

five_c_shaped_proj_tsne_model1_selected <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "b3", 
    cex = 2,
    position = c(0.08, 0.9),
    axis_text_size = 4.5, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")
```

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1.23, 
               scaled_data = scaled_pbmc_data, 
               scaled_data_model = scaled_pbmc_data_model, 
               distance_df_small_edges = tr_from_to_df_pbmc, 
               axis_param = list(limits = 1,
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.48, 
                                 axis_pos_y = -0.48, 
                                 threshold = 0.082))

@@

pbmc_proj_umap_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

@@

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 1.25, 
               scaled_data = scaled_pbmc_data, 
               scaled_data_model = scaled_pbmc_data_model, 
               distance_df_small_edges = tr_from_to_df_pbmc, 
               axis_param = list(limits = 1.35, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.75, 
                                 axis_pos_y = -0.75, 
                                 threshold = 0.12))

@@

pbmc_proj_umap_model2 <- plot_proj(
    proj_obj = proj_obj2, 
    point_param = c(1.5, 0.2), # size, alpha, color
    plot_limits = c(-1, 0.75), 
    title = "a3", 
    cex = 2, 
    axis_text_size = 4,
    is_color = TRUE) + scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

@@

pbmc_proj_tsne_model1_best <- plot_proj(
  proj_obj = proj_obj1,
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  title = "b2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

@@

pbmc_proj_tsne_model2_best <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1, 0.75), 
  title = "b3", 
  cex = 2, 
  axis_text_size = 4,
  is_color = TRUE) + scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))
```

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 2.5, 
               scaled_data = scaled_mnist_data, 
               scaled_data_model = scaled_mnist_data_model, 
               distance_df_small_edges = tr_from_to_df_mnist, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.92, 
                                 axis_pos_y = -0.92, 
                                 threshold = 0.06))

@@

mnist_proj_tsne_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(0.5, 0.5), # size, alpha, color
  line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
  plot_limits = c(-1.1, 0.9), 
  title = "b", 
  cex = 2, 
  axis_text_size = 3.5, 
  is_color = TRUE) +
  scale_color_manual(values = c("#999999",'#ff7f00')) +
  theme(
    legend.position = "none"
  )

mnist_proj_tsne_model1_link <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1.1, 0.9), 
    title = "b", 
    cex = 2.5, 
    axis_text_size = 4.5, 
    is_color = TRUE) +
    scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
    theme(
        legend.position = "none"
    )

@@

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 2, 
               scaled_data = scaled_mnist_data, 
               scaled_data_model = scaled_mnist_data_model, 
               distance_df_small_edges = tr_from_to_df_mnist, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.83, 
                                 axis_pos_y = -0.83, 
                                 threshold = 0.06))

@@

mnist_proj_tsne_model2 <- plot_proj(
    proj_obj = proj_obj2,
    point_param = c(0.5, 0.3), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1, 1), 
    title = "c", 
    cex = 2, 
    axis_text_size = 3.5, 
    is_color = TRUE) +
    scale_color_manual(values = c("#999999",'#ff7f00')) +
    theme(
        legend.position = "none"
    )

mnist_proj_tsne_model2_link <- plot_proj(
    proj_obj = proj_obj2, 
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1, 1), 
    title = "c", 
    cex = 2.5, 
    axis_text_size = 4.5, 
    is_color = TRUE) +
    scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
    theme(
        legend.position = "none"
    )

>>>>

proj_obj1 <- quollr::get_projection(projection = model_prj1, 
               proj_scale = 1, 
               highd_data = scaled_two_curvy_data, 
               model_highd = scaled_two_curvy_data_model, 
               trimesh_data = tr_from_to_df_two_curvy, 
               axis_param = list(limits = 0.5, 
                                 axis_scaled = 2,
                                 axis_pos_x = -0.5, 
                                 axis_pos_y = -0.5, 
                                 threshold = 0.03))

@@

two_curvy_proj_true <- plot_proj(
  proj_obj = proj_obj1_true, 
  point_param = c(0.5, 0.5, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "black"), # linewidth, alpha
  plot_limits = c(-0.6, 0.6), 
  axis_text_size = 4, 
  is_category = FALSE) +
  interior_annotation(label = "a", cex = 1.5) +
  theme(aspect.ratio=1, 
        legend.position = "none")

@@

two_curvy_proj_tsne_first_model1 <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-0.6, 0.6), 
    axis_text_size = 2, 
    is_category = FALSE) +
  interior_annotation(label = "b", position = sc_ltr_pos, cex = 1) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

proj_obj2 <- get_projection(projection = model_prj2, 
                            proj_scale = 1, 
                            highd_data = scaled_two_curvy_data, 
                            model_highd = scaled_two_curvy_data_model, 
                            trimesh_data = tr_from_to_df_two_curvy, 
                            axis_param = list(limits = 0.35, 
                                              axis_scaled = 2,
                                              axis_pos_x = -0.35, 
                                              axis_pos_y = -0.35, 
                                              threshold = 0.01))

@@

two_curvy_proj_true2 <- plot_proj(
    proj_obj = proj_obj2_true, 
    point_param = c(0.5, 0.5, clr_choice), # size, alpha, color
    line_param = c(0.5, 0.5, "black"), # linewidth, alpha
    plot_limits = c(-0.42, 0.42), 
    axis_text_size = 4, 
    is_category = FALSE) +
  interior_annotation(label = "b", cex = 1.5) +
  theme(aspect.ratio = 1, 
        legend.position = "none")

@@

two_curvy_proj_tsne_all_model1 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(0.1, 0.5, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "black"), # linewidth, alpha
  plot_limits = c(-0.5, 0.5), 
  axis_text_size = 2, 
  is_category = FALSE) +
  interior_annotation(label = "c", position = sc_ltr_pos, cex = 1) +
  theme(aspect.ratio = 1) #+
  #geom_segment(
  #  data = model_df, 
  #  aes(
  #    x = proj1_from, 
  #    y = proj2_from, 
  #    xend = proj1_to, 
  #    yend = proj2_to), 
  #  color = "#000000")

@@

algo_obj_two_curvy2 <- fit_highd_model(
  highd_data = training_data_two_curvy, 
  nldr_data = tsne_two_curvy, 
  bin1 = num_bins_x_two_curvy, 
  q = 0.1, 
  benchmark_highdens = 5)

tr_from_to_df_two_curvy2 <- algo_obj_two_curvy2$trimesh_data
df_bin_centroids_two_curvy2 <- algo_obj_two_curvy2$model_2d
df_bin_two_curvy2 <- algo_obj_two_curvy2$model_highd

hex_grid_two_curvy2 <- algo_obj_two_curvy2$hb_obj$hex_poly
counts_df_two_curvy2 <- algo_obj_two_curvy2$hb_obj$std_cts

hex_grid_with_counts_two_curvy2 <- left_join(hex_grid_two_curvy2, counts_df_two_curvy2, by = c("hex_poly_id" = "hexID"))

@@

tr_from_to_df_two_curvy3 <- algo_obj_two_curvy3$tr_from_to_df
df_bin_centroids_two_curvy3 <- algo_obj_two_curvy3$df_bin_centroids
df_bin_two_curvy3 <- algo_obj_two_curvy3$df_bin

hex_grid_two_curvy3 <- algo_obj_two_curvy3$hb_obj$hex_poly
counts_df_two_curvy2 <- algo_obj_two_curvy3$hb_obj$std_cts

hex_grid_with_counts_two_curvy3 <- left_join(hex_grid_two_curvy3, counts_df_two_curvy3, by = c("hex_poly_id" = "hexID"))

@@

<!-- two_curvy_proj_first_model1_umap <- plot_proj( -->
<!--     proj_obj = proj_obj1,  -->
<!--     point_param = c(0.5, 0.2, "#636363"), # size, alpha, color -->
<!--     line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha -->
<!--     plot_limits = c(-0.6, 0.6),  -->
<!--     title = "c2",  -->
<!--     cex = 2,  -->
<!--     position = sc_ltr_pos, -->
<!--     axis_text_size = 4,  -->
<!--     is_category = FALSE) + -->
<!--     theme( -->
<!--         legend.position = "none" -->
<!--     ) -->

@@

<!-- two_curvy_proj_model_delaunay_umap <- plot_proj( -->
<!--     proj_obj = proj_obj1_temp1,  -->
<!--     point_param = c(0.5, 0.2, "#636363"), # size, alpha, color -->
<!--     line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha -->
<!--     plot_limits = c(-0.6, 0.6),  -->
<!--     title = "a2",  -->
<!--     cex = 2,  -->
<!--     position = sc_ltr_pos, -->
<!--     axis_text_size = 4,  -->
<!--     is_category = FALSE) + -->
<!--     theme(aspect.ratio = 1,  -->
<!--           legend.position = "none") -->

@@

<!-- two_curvy_proj_model_benchmark2_umap <- plot_proj( -->
<!--     proj_obj = proj_obj1_temp2,  -->
<!--     point_param = c(0.5, 0.2, "#636363"), # size, alpha, color -->
<!--     line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha -->
<!--     plot_limits = c(-0.6, 0.6),  -->
<!--     title = "b2",  -->
<!--     cex = 2,  -->
<!--     position = sc_ltr_pos, -->
<!--     axis_text_size = 4,  -->
<!--     is_category = FALSE) + -->
<!--     theme(aspect.ratio = 1,  -->
<!--           legend.position = "none") -->

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 2, 
               highd_data = scaled_gau_data, 
               model_highd = scaled_gau_data_model, 
               trimesh_data = tr_from_to_df_gau1, 
               axis_param = list(limits = 1,
                                 axis_scaled = 2,
                                 axis_pos_x = -0.72, 
                                 axis_pos_y = -0.72, 
                                 threshold = 0.1))

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 3, 
                            highd_data = scaled_gau_data, 
                            model_highd = scaled_gau_data_model, 
                            trimesh_data = tr_from_to_df_gau1, 
                            axis_param = list(limits = 1.5,
                                              axis_scaled = 2,
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.05))

five_gau_proj_tsne_model2 <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(1.5, 0.05, clr_choice), # size, alpha, color
  line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
  plot_limits = c(-1.3, 1.3), 
  axis_text_size = 4, 
  is_category = FALSE) +
  interior_annotation(label = "a3", position = c(0.08, 0.9), cex = 1.5) +
  theme(aspect.ratio = 1,
        legend.position = "none") 
```

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 3, 
                            highd_data = scaled_gau_data, 
                            model_highd = scaled_gau_data_model, 
                            trimesh_data = tr_from_to_df_gau1, 
                            axis_param = list(limits = 1.5,
                                              axis_scaled = 2,
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.05))

five_gau_proj_umap_model2 <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(1.5, 0.05, clr_choice), # size, alpha, color
  line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
  plot_limits = c(-1.3, 1.3), 
  axis_text_size = 4, 
  is_category = FALSE) +
  interior_annotation(label = "b3", position = c(0.08, 0.9), cex = 1.5) +
  theme(aspect.ratio = 1,
        legend.position = "none")
```

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 3, 
                            highd_data = scaled_gau_data, 
                            model_highd = scaled_gau_data_model, 
                            trimesh_data = tr_from_to_df_gau1, 
                            axis_param = list(limits = 1.5,
                                              axis_scaled = 2,
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.05))

five_gau_proj_pacmap_model2 <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(1.5, 0.05, clr_choice), # size, alpha, color
  line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
  plot_limits = c(-1.3, 1.3), 
  axis_text_size = 4, 
  is_category = FALSE) +
  interior_annotation(label = "c3", position = c(0.08, 0.9), cex = 1.5) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

proj_obj1 <- get_projection(projection = projection,
                            proj_scale = 1,
                            highd_data = scaled_c_shaped_data,
                            model_highd = scaled_c_shaped_data_model,
                            trimesh_data = tr_from_to_df_dens_clust,
                            axis_param = list(limits = 0.4,
                                              axis_scaled = 3,
                                              axis_pos_x = -0.28,
                                              axis_pos_y = -0.28,
                                              threshold = 0.02))

@@

five_c_shaped_proj_tsne_model1 <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    axis_text_size = 4.5, 
    is_category = TRUE) +
  interior_annotation(label = "a3", position = c(0.08, 0.9), cex = 2) +
  scale_color_manual(values = c('#d9d9d9', '#800026')) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

five_c_shaped_proj_tsne_model1_selected <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    axis_text_size = 4.5, 
    is_category = TRUE) +
  interior_annotation(label = "b3", position = c(0.08, 0.9), cex = 2) +
  scale_color_manual(values = c('#d9d9d9', '#800026')) +
  theme(aspect.ratio = 1,
        legend.position = "none")
```

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1.23, 
               highd_data = scaled_pbmc_data, 
               model_highd = scaled_pbmc_data_model, 
               trimesh_data = tr_from_to_df_pbmc, 
               axis_param = list(limits = 1,
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.48, 
                                 axis_pos_y = -0.48, 
                                 threshold = 0.082))

@@

pbmc_proj_umap_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "a2", cex = 2) + 
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

@@

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 1.25, 
               highd_data = scaled_pbmc_data, 
               model_highd = scaled_pbmc_data_model, 
               trimesh_data = tr_from_to_df_pbmc, 
               axis_param = list(limits = 1.35, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.75, 
                                 axis_pos_y = -0.75, 
                                 threshold = 0.12))

@@

pbmc_proj_umap_model2 <- plot_proj(
    proj_obj = proj_obj2, 
    point_param = c(1.5, 0.2), # size, alpha, color
    plot_limits = c(-1, 0.75), 
    axis_text_size = 4,
    is_category = TRUE) +
  interior_annotation(label = "a3", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

@@

pbmc_proj_tsne_model1_best <- plot_proj(
  proj_obj = proj_obj1,
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-0.65, 0.65), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "b2", cex = 2) +
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))

@@

pbmc_proj_tsne_model2_best <- plot_proj(
  proj_obj = proj_obj2,
  point_param = c(1.5, 0.2), # size, alpha, color
  plot_limits = c(-1, 0.75), 
  axis_text_size = 4,
  is_category = TRUE) +
  interior_annotation(label = "b3", cex = 2) + 
  scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada"))
```

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 2.5, 
               highd_data = scaled_mnist_data, 
               model_highd = scaled_mnist_data_model, 
               trimesh_data = tr_from_to_df_mnist, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.92, 
                                 axis_pos_y = -0.92, 
                                 threshold = 0.06))

@@

mnist_proj_tsne_model1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(0.5, 0.5), # size, alpha, color
  line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
  plot_limits = c(-1.1, 0.9), 
  axis_text_size = 3.5, 
  is_category = TRUE) +
  interior_annotation(label = "b", cex = 2) +
  scale_color_manual(values = c("#999999",'#ff7f00')) +
  theme(
    legend.position = "none"
  )

mnist_proj_tsne_model1_link <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1.1, 0.9), 
    axis_text_size = 4.5, 
    is_category = TRUE) +
  interior_annotation(label = "b", cex = 2.5) +
  scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
  theme(
      legend.position = "none"
  )

@@

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 2, 
               highd_data = scaled_mnist_data, 
               model_highd = scaled_mnist_data_model, 
               trimesh_data = tr_from_to_df_mnist, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.83, 
                                 axis_pos_y = -0.83, 
                                 threshold = 0.06))

@@

mnist_proj_tsne_model2 <- plot_proj(
    proj_obj = proj_obj2,
    point_param = c(0.5, 0.3), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1, 1), 
    axis_text_size = 3.5, 
    is_category = TRUE) +
  interior_annotation(label = "c", cex = 2) +
  scale_color_manual(values = c("#999999",'#ff7f00')) +
  theme(
      legend.position = "none"
  )

mnist_proj_tsne_model2_link <- plot_proj(
    proj_obj = proj_obj2, 
    point_param = c(1.2, 0.5), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-1, 1), 
    axis_text_size = 4.5, 
    is_category = TRUE) +
  interior_annotation(label = "c", cex = 2.5) +
  scale_color_manual(values = c("#d9d9d9",'#ff7f00')) +
  theme(
      legend.position = "none"
  )
